---
title: "Simple Dashboard"
author: "Fotis Sioutas"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill

params:
  magpie_data: NULL
---

```{r loading_required_libraries, include=FALSE}
# Loading required libraries
library(flexdashboard)
library(ggplot2)
library(plotly)
library(magclass)
library(mip)
library(quitte)

# Assign parameter
data <- params$magpie_data
data <- data[c("USA","CHA"),2025:2050,]
names(dimnames(data))[3] <- c("variable.unit")

```

```{r creating_charts, include=FALSE}

  plot <- NULL 

  # CO2 emissions per sector
  vars <- c("Emissions|CO2|Energy|Demand.Mt CO2/yr",
            "Emissions|CO2|Energy|Supply.Mt CO2/yr",
            "Emissions|CO2|Industrial Processes.Mt CO2/yr",
            "Emissions|CO2|AFOLU.Mt CO2/yr")

  CO2emi <- data[, , vars]

  CO2emi <- as.quitte(CO2emi) %>% select(-c(unit, model, scenario))
  
  p <- ggplot(CO2emi, aes(x = period, y = value, fill = variable)) +
    geom_area() +
    facet_wrap(~region) +
    theme_minimal() +
    ylab("Mt CO2/yr")

  plot$CO2emi <- ggplotly(p)

  # CO2 price
  PrC <- data[, , "Price|Carbon.US$2015/tn CO2"]
  
  PrC <- as.quitte(PrC) %>% select(-c(unit, model, scenario))

  p <- ggplot(PrC, aes(x = period, y = value)) +
    geom_line() +
    facet_wrap(~region) +
    theme_minimal() +
    ylab("US$2015/tn CO2")

  plot$CO2price <- ggplotly(p)
  
  # Electricity mix
  vars <- c("Secondary Energy|Electricity|Biofuels|w/ CCS.TWh",
            "Secondary Energy|Electricity|Biofuels|w/o CCS.TWh",
            "Secondary Energy|Electricity|Coal|w/ CCS.TWh",
            "Secondary Energy|Electricity|Coal|w/o CCS.TWh",
            "Secondary Energy|Electricity|Gas|w/ CCS.TWh",
            "Secondary Energy|Electricity|Gas|w/o CCS.TWh",
            "Secondary Energy|Electricity|Heat.TWh",
            "Secondary Energy|Electricity|Geothermal and other renewable sources.TWh",
            "Secondary Energy|Electricity|Hydro.TWh",
            "Secondary Energy|Electricity|Hydrogen.TWh",
            "Secondary Energy|Electricity|Nuclear.TWh",
            "Secondary Energy|Electricity|Oil.TWh",
            "Secondary Energy|Electricity|Oil|w/o CCS.TWh",
            "Secondary Energy|Electricity|Wind.TWh",
            "Secondary Energy|Electricity|Solar.TWh")
  
  elMix <- data[, , vars]
  
  elMix <- as.quitte(elMix) %>% select(-c(unit, model, scenario))
  
  p <- ggplot(elMix, aes(x = period, y = value, fill = variable)) +
    geom_area() +
    facet_wrap(~region) +
    theme_minimal() +
    ylab("Secondary Energy|Electricity.TWh")
  
  plot$electricityMix <- ggplotly(p)

```

<!--############################# -->

<!--#### START OF MENUS CODE #### -->

<!--############################# -->

<!-- ### Creating main emissions menu ### -->

<!--Creating First Page - Emissions Page-->

# Emissions {#emissions data-icon="glyphicon glyphicon-stats"}

## Side Navigation {.sidebar data-width="60"}

[ ](#emissions){.glyphicon .glyphicon-stats .sidebar-button .selected} [ ](#emissions-prices){.glyphicon .glyphicon-eur .sidebar-button}

<!-- Dividing the page in two columns-->

## Column

<!-- creating a container to show the emissions quantitites-->

### Emissions quantity

```{r}
ggplotly(plot$CO2emi)
```

<!-- Second column-->

## Column

<!-- creating two additional containers in the second column to show extra information-->

### Emissions quantities empty container 1

```{r}
```

### Emissions quantities empty container 2

```{r}
```

<!-- Creating second page with emissions prices-->

# Emissions Prices {#emissions-prices .hidden data-icon="glyphicon glyphicon-eur"}

## Side Navigation {.sidebar data-width="60"}

[ ](#emissions){.glyphicon .glyphicon-stats .sidebar-button} [ ](#emissions-prices){.glyphicon .glyphicon-eur .sidebar-button .selected}

## Column

<!-- dividing the page into two containers and showing prices chart in the second one-->

### Emissions prices empty container 1

```{r}
```

### Emissions prices

```{r}
ggplotly(plot$CO2price)
```

<!-- ### Creating electricity sector main menu ### -->

# Electricity sector {data-icon="glyphicon glyphicon-scale"}

<!-- dividing the page into two containers and showing the eelectricity sector chart in the first one -->

<!-- creating a container to show the emissions quantitites-->

### Electricity mix empty container 1

```{r}
```

<!-- creating a container to show the emissions quantitites-->

### Electricity mix

```{r}
ggplotly(plot$electricityMix)
```

<!-- ADVANCED: using CSS to define the appearance of the side bar -->

<!-- CSS -->

```{=html}
<style type="text/css">

  .sidebar-button {  /* sidebar size  */
     display: inline-block;
     font-size: 40px;
     height: 80px;
     padding-top: 20px
  }
  
  .sidebar-button, .sidebar-button:hover {
    text-decoration: none;
  }
  
  .sidebar-button.selected, .sidebar-button.selected:hover {
    opacity: 1;
  }
  
  .sidebar-button {
    opacity: 0.7;
  }
  
  .sidebar-button:hover {
    opacity: 0.4;
  }

</style>
```
